Reproductive Allocation Calculations

### 2014-09-13 docs/CarbonInvestments.tex
Update for flower style position for the BAER. Map is still to be changes.

\clearpage
\newpage
\section{BAER}
\begin{multicols}{2}
\includegraphics[width=3in]{BAER.png}
\vfill
\columnbreak
\input{../output/docs/BAER.tex}
\\Comments:
\begin{itemize}
\item \textbf{Fruits just collected and weights will be added soon.
Need to still collect finished flower stigma (didn't realize this) and seed pods}
\end{itemize}
\end{multicols}

\clearpage
\newpage
\section{BOLE}
\begin{multicols}{2}
\includegraphics[width=3in]{BOLE.png}
\vfill
\columnbreak
\input{../output/docs/BOLE.tex}
\\Comments:
\begin{itemize}
\item Missing measurements.
\item Presumably some derivative calculations are necessary for some categories.
\end{itemize}
\end{multicols}

@@

\section{COER}
\begin{multicols}{2}
\includegraphics[width=2.7in]{COER.png}
\vfill
\columnbreak
\input{../output/docs/COER.tex}
\\Comments:
\begin{itemize}
\item Missing measurements.
\end{itemize}
\end{multicols}

@@

\section{EPMI}
\begin{multicols}{2}
\includegraphics[width=2.5in]{EPMI.png}
\vfill
\columnbreak
\input{../output/docs/EPMI.tex}
\\Comments:
\begin{itemize}
\item OK.
\end{itemize}
\end{multicols}

@@

\input{../output/docs/GRBU.tex}\\
Comments:
\begin{itemize}
\item Missing measurements.
\item Otherwise OK.
\end{itemize}

@@

\input{../output/docs/GRSP.tex}
\\Comments:
\begin{itemize}
\item Missing measurments
\end{itemize}

@@

\clearpage
\newpage
\section{HATE}
\begin{multicols}{2}
\includegraphics[width=3in]{HATE.png}
\vfill
\columnbreak
\input{../output/docs/HATE.tex}
\\Comments:
\begin{itemize}
\item Missing measurements.
\end{itemize}

@@

\section{HEPU}
\begin{multicols}{2}
\includegraphics[width=3in]{HEPU.png}
\vfill
\columnbreak
\input{../output/docs/HEPU.tex}
\\Comments:
\begin{itemize}
\item Warning: fruit large immature = fruit mature
\item Error: Fruit aborted $<$ fruit large immature
\item Otherwise ok.
\end{itemize}
\end{multicols}

@@

\section{LEES}
\begin{multicols}{2}
\includegraphics[width=3in]{LEES.png}
\vfill
\columnbreak
%%%%
\input{../output/docs/LEES.tex}
%%%%%
\\
Comments:
\begin{itemize}
\item  OK.
\end{itemize}
\end{multicols}
\clearpage
\newpage

\section{PELA}
\begin{multicols}{2}
\includegraphics[width=2.8in]{PELA.png}
\vfill
\columnbreak
\input{../output/docs/PELA.tex}
\\Comments:
\begin{itemize}
\item Missing measurements.
\end{itemize}

\clearpage
\newpage
\section{PEPU}
\begin{multicols}{2}
\includegraphics[width=2.7in]{PEPU.png}
\vfill
\columnbreak
\input{../output/docs/PEPU.tex}
\\Comments:
\begin{itemize}
\item Missing measurements. \textbf{To be collected}.
\end{itemize}

\end{multicols}
\clearpage
\newpage

\clearpage
\newpage
\section{PHPH}
\begin{multicols}{2}
\includegraphics[width=3in]{PHPH.png}
\vfill
\columnbreak
\input{../output/docs/PHPH.tex}
\\Comments:
\begin{itemize}
\item Missing measurements. \textbf{To be collected}.
\end{itemize}
\end{multicols}

\clearpage
\newpage
\section{PILI}
\begin{multicols}{2}
\includegraphics[width=2.7in]{PILI.png}
\vfill
\columnbreak
\input{../output/docs/PILI.tex}
\\Comments:
\begin{itemize}
\item No measurements for "seed aborted".
\item Otherwise ok.
\end{itemize}
\end{multicols}

\clearpage
\newpage
\section{PUTU}
\begin{multicols}{2}
\includegraphics[width=2.5in]{PUTU.png}
\vfill
\columnbreak
\input{../output/docs/PUTU.tex}
\\Comments:
\begin{itemize}
\item OK
\end{itemize}
\end{multicols}

>>>>

\clearpage
\newpage
\section{BAER}
\begin{multicols}{2}
\includegraphics[width=3in]{BAER.png}
\vfill
\columnbreak
\input{../output/docs/BAER.tex}
\end{multicols}

\clearpage
\newpage
\section{BOLE}
\begin{multicols}{2}
\includegraphics[width=3in]{BOLE.png}
\vfill
\columnbreak
\input{../output/docs/BOLE.tex}
\end{multicols}

@@

\section{COER}
\begin{multicols}{2}
\includegraphics[width=2.7in]{COER.png}
\vfill
\columnbreak
\input{../output/docs/COER.tex}
\end{multicols}

@@

\section{EPMI}
\begin{multicols}{2}
\includegraphics[width=2.5in]{EPMI.png}
\vfill
\columnbreak
\input{../output/docs/EPMI.tex}
\end{multicols}

@@

\input{../output/docs/GRBU.tex}\\

@@

\input{../output/docs/GRSP.tex}

@@

\clearpage
\newpage
\section{HATE}
\begin{multicols}{2}
\includegraphics[width=3in]{HATE.png}
\vfill
\columnbreak
\input{../output/docs/HATE.tex}

@@

\section{HEPU}
\begin{multicols}{2}
\includegraphics[width=3in]{HEPU.png}
\vfill
\columnbreak
\input{../output/docs/HEPU.tex}
\end{multicols}

@@

\section{LEES}
\begin{multicols}{2}
\includegraphics[width=3in]{LEES.png}
\vfill
\columnbreak
%%%%
\input{../output/docs/LEES.tex}
%%%%%
\\
\end{multicols}
\clearpage
\newpage

\section{PELA}
\begin{multicols}{2}
\includegraphics[width=2.8in]{PELA.png}
\vfill
\columnbreak
\input{../output/docs/PELA.tex}
\end{multicols}

\clearpage
\newpage
\section{PEPU}
\begin{multicols}{2}
\includegraphics[width=2.7in]{PEPU.png}
\vfill
\columnbreak
\input{../output/docs/PEPU.tex}
\end{multicols}
\clearpage
\newpage

\clearpage
\newpage
\section{PHPH}
\begin{multicols}{2}
\includegraphics[width=3in]{PHPH.png}
\vfill
\columnbreak
\input{../output/docs/PHPH.tex}
\end{multicols}

\clearpage
\newpage
\section{PILI}
\begin{multicols}{2}
\includegraphics[width=2.7in]{PILI.png}
\vfill
\columnbreak
\input{../output/docs/PILI.tex}
\end{multicols}

\clearpage
\newpage
\section{PUTU}
\begin{multicols}{2}
\includegraphics[width=2.5in]{PUTU.png}
\vfill
\columnbreak
\input{../output/docs/PUTU.tex}
\end{multicols}
